\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-23 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Enfin le graphique 4 !
Cela a été compliqué, car il faut prendre en compte terme_Adoll et prix_fob pour faire le terme_A.
Figure 5 ! On les grignote...

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects)}
\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=4in]
{graph_composition_all.pdf}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem air freight} & {\small (b) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.pdf}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.pdf} \\
{\small (c) Ad-valorem air freight} & {\small (d) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small As indices with reference value 100 in 1974} }\\
\includegraphics[width=2.5in, height=2in]{figure5_comme_hummels_base100.pdf}
& \includegraphics[width=2.5in,height=2in]{figure6_comme_hummels_base100.pdf} \\
\end{tabular}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects)}
\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=4in]
{graph_composition_all.jpg}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem air freight} & {\small (b) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.jpg}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.jpg} \\
{\small (c) Ad-valorem air freight} & {\small (d) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small As indices with reference value 100 in 1974} }\\
\includegraphics[width=2.5in, height=2in]{figure5_comme_hummels_base100.jpg}
& \includegraphics[width=2.5in,height=2in]{figure6_comme_hummels_base100.jpg} \\
\end{tabular}
\end{center}
\end{figure}
